Music adaptation: Analysis

### 2022-10-11 analysis/baseline.Rmd
update plots and stats
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# IOI 
## 1. Individual
```{r ioi}
# for each individual
dt_ioi$Articulation <- factor(dt_ioi$Articulation, c("Present", "Absent", "Baseline"))
dt_ioi$Dynamics <- factor(dt_ioi$Dynamics, c("Present", "Absent", "Baseline"))

@@

```{r}
aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

@@

```{r}
aov_ez(
  data = ioi[Category == "both" | Category == "none" | Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

@@

```{r kot-all-plot, echo = FALSE}
ggplot(kot[Subcomponent1 == "Legato"], aes(x = Articulation, y = Mean, color = Dynamics))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  #geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent1) +
  theme_pubr()

ggplot(kot[Subcomponent1 == "Staccato"], aes(x = Articulation, y = Mean, color = Dynamics))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  #geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent1) +
  theme_pubr()

@@

```{r}
aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```
2) Category: All

@@

vel <- vel_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel, "SubNr", "Dynamics", "Articulation", "Category")
vel
```

@@

```{r vel-all-plot,  echo = FALSE}
ggplot(vel, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(binaxis = "y", stackdir = "center", position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2) +
  theme_pubr()

@@

1) Forte

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Forte"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

2) Piano

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Piano"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

@@

## 2. All - group
```{r vel-diff-all, echo = FALSE}
# group mean
vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean), SEM = sd(Mean)/sqrt(.N), Median = median(Mean), IQR = IQR(Mean)), by = .(Articulation, Dynamics, Category, Subcomponent2)]
vel_diff_all
```

@@

```{r vel-diff-all-plot,  echo = FALSE}
ggplot(vel_diff, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(binaxis = "y", stackdir = "center", position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2) +
  theme_pubr()

@@

1) FtoP

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

2) PtoF

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
```

>>>>

# IOI 
## 1. Individual

```{r ioi}
# for each individual
dt_ioi$Articulation <- factor(dt_ioi$Articulation, c("Present", "Absent", "Baseline"))
dt_ioi$Dynamics <- factor(dt_ioi$Dynamics, c("Present", "Absent", "Baseline"))

@@

```{r}
ioi_ca_all_aov <- aov_ez(
  data = ioi,
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

pairs(emmeans(ioi_ca_all_aov, "Category"), adjust = "tukey")
```

@@

```{r}
ioi_ca_par_aov <- aov_ez(
  data = ioi[Category == "both" | Category == "none" | Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)

pairs(emmeans(ioi_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r kot-all-plot, echo = FALSE}
ggplot(kot, aes(x = Articulation, y = Mean, color = Dynamics))+
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent1, labeller = as_labeller(c("Legato" = "Legato/Forte", "Staccato" = "Staccato/Piano"))) +
  theme_pubr()

@@

```{r}
aov_ez(
  data = kot[Subcomponent1 == "Staccato" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

@@

vel <- vel_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Articulation, Dynamics, Category, Subcomponent2)]
setorder(vel, "Subcomponent2", "SubNr", "Dynamics", "Articulation", "Category")
vel
```

@@

```{r vel-all-plot,  echo = FALSE}
ggplot(vel, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(binaxis = "y", stackdir = "center", position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2, labeller = as_labeller(c("Forte" = "Forte/Legato", "Piano" = "Piano/Staccato"))) +
  theme_pubr()

@@

## 4. Stats
### Forte

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

```{r}
for_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
for_ca_all_aov

pairs(emmeans(for_ca_all_aov, "Category"), adjust = "tukey")
```

3) Category: both vs. art_only vs. baseline

```{r}
for_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Forte" & Category == "both" | Subcomponent2 == "Forte" & Category == "art_only" | Subcomponent2 == "Forte" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
for_ca_par_aov

pairs(emmeans(for_ca_par_aov, "Category"), adjust = "tukey")
```

### Piano

```{r}
aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```
2) Category: All

```{r}
pia_ca_all_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
pia_ca_all_aov

pairs(emmeans(pia_ca_all_aov, "Category"), adjust = "tukey")
```

3) Category: both vs. art_only vs. baseline

```{r}
pia_ca_par_aov <- aov_ez(
  data = vel[Subcomponent2 == "Piano" & Category == "both" | Subcomponent2 == "Piano" & Category == "art_only" | Subcomponent2 == "Piano" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
pia_ca_par_aov

pairs(emmeans(pia_ca_par_aov, "Category"), adjust = "tukey")
```

@@

```{r vel-diff-all, echo = FALSE}
# group mean
vel_diff_all <- vel_diff[, .(N = .N, Mean = mean(Mean), SD = sd(Mean), SEM = sd(Mean)/sqrt(.N), Median = median(Mean), IQR = IQR(Mean)), by = .(Articulation, Dynamics, Category, Subcomponent2)]
vel_diff_all
```

@@

```{r vel-diff-all-plot,  echo = FALSE}
ggplot(vel_diff, aes(x = Dynamics, y = Mean, color = Articulation))+ 
  geom_boxplot(position = position_dodge2(preserve = "single")) +
  geom_point(position = position_dodge(0.75)) +
  facet_grid( ~ Subcomponent2, labeller = as_labeller(c("FtoP" = "FtoP/PtoF", "PtoF" = "PtoF/StoL"))) +
  theme_pubr()

@@

## 4. Stats
### FtoP

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

```{r}
ftop_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_all_aov

pairs(emmeans(ftop_ca_all_aov, "Category"), adjust = "tukey")
```

3) Category: both vs. art_only vs. baseline

```{r}
ftop_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_par_aov

pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```

### PtoF

```{r}
aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF" & Category != "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Articulation", "Dynamics")
)
```

```{r}
ptof_ca_all_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "PtoF"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ptof_ca_all_aov

pairs(emmeans(ptof_ca_all_aov, "Category"), adjust = "tukey")
```

3) Category: both vs. art_only vs. baseline

```{r}
ftop_ca_par_aov <- aov_ez(
  data = vel_diff[Subcomponent2 == "FtoP" & Category == "both" | Subcomponent2 == "FtoP" & Category == "art_only" | Subcomponent2 == "FtoP" & Category == "baseline"],
  id = "SubNr",
  dv = "Mean",
  within = c("Category")
)
ftop_ca_par_aov

pairs(emmeans(ftop_ca_par_aov, "Category"), adjust = "tukey")
```
